Title

### 2011-09-29 inc/ms_model/ms_model.tex
worked out some teething issues for import package

For a classical set of $N$ particles (labelled $i$), distributed 6D space (3 position, 3 momentum) by 
\begin{gather}
  f_{\smallD}(\vec{r}, \vec{p}; t) = 
  \sum\limits^{N}_{i=1} \delta(\vec{r}_{i} - \vec{r}) \delta(\vec{p}_{i} - \vec{p}) \\
  \text{which satisfies} \quad \int d^{3}x\,d^{3}p \; f_{\smallD}(\vec{r}, \vec{p}; t) = N
\end{gather}
of mass $m$ which interact with some potential $V(\vec{r}_{i} - \vec{r}_{j})$, their motion is governed by the equations
\begin{subequations}\label{eq:std_motion}
\begin{gather}
  \frac{d\vec{r}_{i}(t)}{dt} = \frac{\vec{p}_{i}(t)}{m}\\
  \frac{d\vec{p}_{i}(t)}{dt} = -\sum\limits_{j} \frac{d}{d\vec{r}_{i}} V(\vec{r}_{i} - \vec{r}_{j})
\end{gather}
\end{subequations}
Now consider the time evolution of $f_{\smallD}$
\begin{equation}
  \frac{\partial f_{\smallD}}{\partial t} = 
  \frac{d\vec{r}}{dt} \frac{\partial f_{\smallD}}{\partial \vec{r}} 
  + \frac{\partial f_{\smallD}}{\partial \vec{p}} \frac{d\vec{p}}{dt}
\end{equation}
but with \ref{eq:std_motion} the final discreet evolution equation is
%TODO find missing minus sign!
\begin{equation}
  \frac{d}{dt} f_{\smallD}(\vec{r}, \vec{p}; t) =
  -\frac{\vec{p}}{m} \frac{\partial}{\partial \vec{r}} f_{\smallD}(\vec{r}, \vec{p}; t)
  + \frac{\partial}{\partial \vec{p}} f_{\smallD} (\vec{r}, \vec{p}; t)
  \frac{\partial}{\partial \vec{r}} \iint d\vecprime{r} d\vecprime{p} V(\vec{r} - \vecprime{r}) f_{\smallD}(\vecprime{r},\vecprime{p};t)
\end{equation}
%TODO ensemble av and mean-field
Final equation:
\begin{equation} \label{eq:formal_evolution}
  \frac{d}{dt} f(\vec{r}, \vec{p}; t) =
  -\frac{\vec{p}}{m} \frac{\partial}{\partial \vec{r}} f(\vec{r}, \vec{p}; t)
  + \frac{\partial}{\partial \vec{p}} f (\vec{r}, \vec{p}; t)
  \frac{\partial}{\partial \vec{r}} \iint d\vecprime{r} d\vecprime{p} V(\vec{r} - \vecprime{r}) f(\vecprime{r},\vecprime{p};t)
\end{equation}

@@

The formal evolution explored in \cite{sec:formal_evolution} allows for any distribution function.
For Ultrafast Electron Microscopy, the electron pulse is generated by a laser pulse, therefore the electron pulse can be thought to be a Gaussian, mimicing the laser pulse for which generated it.
How correct this assumption is will be explored in \ref{sec:initial_conditions}.
In this section we consider a Gaussian distribution function, generally of the form
\begin{equation}
  f(\vec{r}, \vec{p}; t) = C(t)\exp \left[ - \Gamma(\vec{r}, \vec{p}; t) \right]
\end{equation}
where in this case we choose the argument (i.e. the function $\Gamma$) as
\begin{equation}
  \Gamma(\vec{r}, \vec{p}; t) =
  \frac{x^2 + y^2}{2 \sigma_{\smallT}} + \frac{z^2}{2 \sigma_{z}}
  + \frac{
    [p_x - (\gamma_{\smallT}/\sigma_{\smallT}) x ]^2 
    + [p_y - (\gamma_{\smallT}/\sigma_{\smallT}) y ]^2
  }{2 \eta_{\smallT}}
  + \frac{ [p_z - (\gamma_{z}/\sigma_{z}) z ]^2 }{2 \eta_{z}}
\end{equation}
This parameterization defines the spatial uncertainty $\sigma$, the local momentum uncertainty $\eta$, and the momentum chirp $\gamma$ in each spatial direction.
The ``chirp'' of a pulse quantifies the difference in local momentum from one side of the pulse to the other.
For example, in a pulse which is normally (positively) chirped longitudinally, the front of the pulse with be moving faster than the back.

>>>>

For a classical set of $N$ particles (labelled by the index $i$), distributed 6D space (3 position, 3 momentum) by 
\begin{gather}
  f_{\smallD}(\vec{r}, \vec{p}; t) = 
  \sum\limits^{N}_{i=1} \delta(\vec{r}_{i} - \vec{r}) \delta(\vec{p}_{i} - \vec{p}) \\
  \text{which satisfies} \quad \int d^{3}x\,d^{3}p \; f_{\smallD}(\vec{r}, \vec{p}; t) = N
\end{gather}
of mass $m$ which interact with some potential $V(\vec{r}_{i} - \vec{r}_{j})$, their motion is governed by the equations
\begin{subequations}\label{eq:std_motion}
\begin{gather}
  \frac{d\vec{r}_{i}(t)}{dt} = \frac{\vec{p}_{i}(t)}{m}\\
  \frac{d\vec{p}_{i}(t)}{dt} = -\sum\limits_{j} \frac{d}{d\vec{r}_{i}} V(\vec{r}_{i} - \vec{r}_{j})
\end{gather}
\end{subequations}
Now consider the time evolution of $f_{\smallD}$
\begin{equation}
  \frac{\partial f_{\smallD}}{\partial t} = 
  \frac{d\vec{r}}{dt} \frac{\partial f_{\smallD}}{\partial \vec{r}} 
  + \frac{\partial f_{\smallD}}{\partial \vec{p}} \frac{d\vec{p}}{dt}
\end{equation}
but with \ref{eq:std_motion} the final discreet evolution equation is
%TODO find missing minus sign!
\begin{equation}
  \frac{d}{dt} f_{\smallD}(\vec{r}, \vec{p}; t) =
  -\frac{\vec{p}}{m} \frac{\partial}{\partial \vec{r}} f_{\smallD}(\vec{r}, \vec{p}; t)
  + \frac{\partial}{\partial \vec{p}} f_{\smallD} (\vec{r}, \vec{p}; t)
  \frac{\partial}{\partial \vec{r}} \iint d\vecprime{r} d\vecprime{p} V(\vec{r} - \vecprime{r}) f_{\smallD}(\vecprime{r},\vecprime{p};t)
\end{equation}
%TODO ensemble av and mean-field
Final equation:
\begin{equation} \label{eq:formal_evolution}
  \frac{d}{dt} f(\vec{r}, \vec{p}; t) =
  -\frac{\vec{p}}{m} \frac{\partial}{\partial \vec{r}} f(\vec{r}, \vec{p}; t)
  + \frac{\partial}{\partial \vec{p}} f (\vec{r}, \vec{p}; t)
  \frac{\partial}{\partial \vec{r}} \iint d\vecprime{r} d\vecprime{p} V(\vec{r} - \vecprime{r}) f(\vecprime{r},\vecprime{p};t)
\end{equation}

@@

The formal evolution explored in \ref{sec:formal_evolution} allows for any distribution function.
For Ultrafast Electron Microscopy, the electron pulse is generated by a laser pulse, therefore the electron pulse can be thought to be a Gaussian, mimicing the laser pulse for which generated it.
How correct this assumption is will be explored in \ref{sec:initial_conditions}.
In this section we consider a Gaussian distribution function, generally of the form
\begin{equation}
  f(\vec{r}, \vec{p}; t) = C(t)\exp \left[ - \Gamma(\vec{r}, \vec{p}; t) \right]
\end{equation}
where in this case we choose the argument (i.e. the function $\Gamma$) as
\begin{equation}
  \Gamma(\vec{r}, \vec{p}; t) =
  \frac{x^2 + y^2}{2 \sigma_{\smallT}} + \frac{z^2}{2 \sigma_{z}}
  + \frac{
    [p_x - (\gamma_{\smallT}/\sigma_{\smallT}) x ]^2 
    + [p_y - (\gamma_{\smallT}/\sigma_{\smallT}) y ]^2
  }{2 \eta_{\smallT}}
  + \frac{ [p_z - (\gamma_{z}/\sigma_{z}) z ]^2 }{2 \eta_{z}}
\end{equation}
This parameterization defines the spatial uncertainty $\sigma$, the local momentum uncertainty $\eta$, and the momentum chirp $\gamma$ in each spatial direction.
The ``chirp'' of a pulse quantifies the difference in local momentum from one side of the pulse to the other.
For example, in a pulse which is normally (positively) chirped longitudinally, the front of the pulse with be moving faster than the back.
